---
title: "Salamanders"
author: "Janelle Christensen & Lauren Manzo"
date: "11/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(janitor)
```

```{r}

# ------------
# Read in csv file
# ------------

salamander_df <- read_csv("mack_creek_vertebrates.csv") %>% 
  clean_names()

```

### Introduction

### Data and Methods

### Results

#### A

Visually compare annual salamander counts in old growth (OG) and clear cut (CC) sections of Mack Creek.

To do:
- finalized graph is a line graph

```{r}

```

#### B

Table of 2017 salamander counts by channel classification (pool, cascades and side-channel) in old growth (OG) and clear cut (CC) sections of Mack Creek.

```{r}

```

#### C

Using the 2017 counts found in Results B above, answer: is there a significant difference in where in the channel Pacific giant salamanders are located (pool, cascade or side channel) between the two sections (old growth and clear cut)?

```{r}

```

#### D

Compare weights of Pacific giant salamanders in clear cut and old growth forest sections of the creek in 2017.

To do:
- Histogram
- qqplot

```{r}

```

#### E

Compare weights of Pacific giant salamanders in pools, cascades and side-channels of Mack Creek in 2017.

To do:
- Exclude from final data, but visually explore
  - Histogram
  - qqplot

```{r}

```


### Summary

- Bullet points

### References

^1^Gregory S. V. 2016. Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present. Environmental Data Initiative. https://doi.org/10.6073/pasta/5de64af9c11579266ef20da2ff32f702. Dataset accessed 11/19/2019.
